Title?

### 2016-08-01 draft.tex
modified equations to make easier to read
did some on results

\subsection{Decay limit}
The constraint from the streaming limit above provides an upper bound on the allowed coupling (or lower bound on the excluded coupling) by considering the production on the $A'$. Naively it might be expected that this suffices, in that all higher couplings are excluded. However, in order to function as a cooling channel, enough of the produced dark gauge bosons must escape the supernova. As the coupling increases, so do processes that prevent the escape, and so the excluded region has an upper bound, above which the luminosity again drops below the neutrino luminosity. The first such limit may be found by considering decay of the dark bosons into Standard Model particles, and assuming that these SM particles are trapped in the supernova core and contribute nothing to the cooling. The dark boson has a typical lifetime of 
\beq
l = \frac{3 E_{A}}{N_{eff} m_A^2 \epsilon^2},
\eeq
and so the fraction escaping the supernova before decaying is given by 
\beq
e^{\frac{r_{decay}}{l}} = e^{\frac{r_{decay} N_{eff} m_A^2 \epsilon^2}{3 E_A}}.
\eeq
To take this into account, the above exponential factor is simply appended to the phase space integrand, and the calculation then proceeds as before. The limit is derived from the same equation, with the only complication being the fact that $ I_A $ is now a function of $ \epsilon $, in addition to $ m_A, T $. This makes the numerical calculation slightly more complicated, but otherwise changes nothing of importance, with now the constraint a transcendental equation,  
\beq
\epsilon \le \sqrt{\frac{4.1 * 10^{37} MeV^2}{I_A(m_A, T, \epsilon)}}.
\eeq

@@

>>>>

\subsection{Decay limit}
The constraint from the streaming limit above provides an upper bound on the allowed coupling (or lower bound on the excluded coupling) by considering the production on the $A'$. Naively it might be expected that this suffices, in that all higher couplings are excluded. However, in order to function as a cooling channel, enough of the produced dark gauge bosons must escape the supernova. As the coupling increases, so do processes that prevent the escape, and so the excluded region has an upper bound, above which the luminosity again drops below the neutrino luminosity. The first such limit may be found by considering decay of the dark bosons into Standard Model particles, and assuming that these SM particles are trapped in the supernova core and contribute nothing to the cooling. The dark boson has a typical lifetime of 
\beq
l = \frac{3 E_{A}}{N_{eff} m_A^2 \epsilon^2},
\eeq
and so the fraction escaping the supernova before decaying is given by 
\beq
e^{r_{decay}/l} = e^{r_{decay} N_{eff} m_A^2 \epsilon^2/(3 E_A)}.
\eeq
To take this into account, the above exponential factor is simply appended to the phase space integrand, and the calculation then proceeds as before. The limit is derived from the same equation, with the only complication being the fact that $ I_A $ is now a function of $ \epsilon $, in addition to $ m_A, T $. This makes the numerical calculation slightly more complicated, but otherwise changes nothing of importance, with now the constraint a transcendental equation,  
\beq
\epsilon \le \sqrt{\frac{4.1 \times 10^{37} MeV^2}{I_A(m_A, T, \epsilon)}}.
\eeq

@@

Both approaches produce constraints that are significantly weaker than the previous work, and that largely reproduce constraints already obtained from beam dump experiments. The squared matrix element obtained from the full one-pion-exchange in the end agrees quite well with that obtained using the approximations appropriate for axionic calculations; the reduction in the bremsstrahlung rate apparently results from significant changes to the phase space when the exact kinematics are used. The effective field theory calculation weakens the constraint by a further order of magnitude, and this difference between the EFT and OPE constraints results only from a difference in the matrix element calculated from each. It's well-known that the OPE model ignores effects related to chiral symmetry, and these evidently serve to reduce the bremsstrahlung rate considerably. Although there is some question as to the applicability of the simple pionless EFT at the highest masses considered, but at that point even significant deviation would not change the overall conclusion.
